Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density \thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-05-31 manuscript.tex
sec 3 updates

When working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique is used \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction}, that accounts for stellar activity, is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible. This problem is known in statistics with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citet{belsley1991}. \xavier{It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF. However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided. Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.}

>>>>

\jessi{Is the following paragraph needed?  Is any model selection actually carried out here?  It seems the model of Eq.~\ref{eq:RV:correction} is fit, and then the significance of the variables are discussed, but no attempts are really made to remove/add/step through the various model options.  The point about multicollinearity is probably good to keep though.} 
When working with a linear regression, there are several ways to select the variables to include in the model. While usually the stepwise technique is used \citep{efroymson1960multiple,hocking1976biometrics}, the proposed function defined in Eq.~\ref{eq:RV:correction}, that accounts for stellar activity, is the result of statistical and astronomical considerations. In particular we checked that the correlations between the proposed parameters were not approaching one: if it was the case, the matrix needed to calculate the estimates would be singular, hence non invertible. This problem is known in statistics with the term multicollinearity. A detailed discussion of the topic can be found in the book by \citet{belsley1991}. It is common to see some correlation between the amplitude parameter $A$ and the FWHM (or SN FWHM) of the CCF. However, in the analysis of real data presented in this work, we never observed a correlation coefficient exceeding $0.66$ and therefore, the problem of multicollinearity is avoided. Finally, we investigate as well the statistical significant of the interaction term between $A$ and the width, and $A$ and the asymmetry of the CC, however, those interaction were relevant for accounting for stellar signal.
